%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------

\cventry
{ Senior Staff Engineer (Kafka)\newline Senior Kafka Administrator\newline Kafka Administrator} % Job title
{Wavelo (Tucows)} % Organization
{Toronto, ON} % Location
{May. 2022 - Present\newline Aug. 2021 - May. 2022\newline Nov. 2020 - Aug. 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Built, secured, and maintained the overall Kafka infrastructure.}
\item {Built the automation to provision, maintain, and monitor all aspects of the Kafka environment via infrastructure as code. (HashiCorp Stack)}
\item {Designed, implemented, and operated multi-datacenter Kafka infrastructure along-side kafka add-ons such as Confluent Schema Registry, MirrorMaker2, Kafka Connect.}
\item {Build monitoring dashboards and visualization to provide real-time insights and observability of Kafka clusters connectivity, security and performance. (DataDog, ElasticSearch, Prometheus, Grafana)}
\item {Built self-serve GitOps tools to increase speed and productivity of developers using the kafka platform. (Topic Management, ACL Management, Kafka Connect Cluster Deployment, KSQL Deployment, Self-Hosted GitHub Runners, etc... )}
\item {Increased our PaaS offerings by building an in-house CLI to interact with our private cloud infrastructure to deal with secret management, volume management, application deployment. (Typer CLI, Nomad APIs, Vault APIs)}
\item {Identified bottlenecks and tune to optimize Kafka performance and throughput.}
\item {Ensured all disaster recovery protocols are tested with routine backup and recovery exercises.}
\end{cvitems}
}

\cventry
{Senior Application Developer \newline Developer} % Job title
{BMO Financial Group} % Organization
{Toronto, ON} % Location
{Oct. 2020 - Oct. 2020 \newline Sept. 2018 - Oct. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Key contributor to the banks customer intellegience platform; Responsible for deriving and implementing a solution which will help provide the business with a complete view of their customers and to deliver pleasent experiences in near real-time} 
\item {Onboarded, trained, and mentored new developers, ensuring they are comfortable and self sufficient in dealing large distributed systems. Adhering to all best practices in code management (Adopting Git Flow), code deployment (Dockerizing your applications), as well as EDA (Event-Driven Architecture).}
\item {Designed \& implemented a real-time data pipeline that is field level encrypted to allow for data transfer between our kafka cluster on-premises and our kafka cluster in the cloud(AWS).}
\item {Helped build real-time streaming data pipelines to reliably get data between systems and applications.}
\item {Built real-time streaming applications that transform \& react to streams of data.}
\item {Automated approaches to streamline and integrate technological processes and/or systems to improve operational efficiency and effectiveness.}
\item {Conceived and wrote detailed software implementations while ensuring that their code adhere to the security, logging, error handling, and performance standards and non-functional requirements.}
\item {Demonstrated detailed application of software knowledge through the production of a series of projects including: \\Application Development (Java, KafkaStreams, KafkaConnect); Other (XSLT/XML, JSON, AVRO, WSDL, HTML, CSS3, Javascript, React, Git, Ansible, Bamboo);}
\end{cvitems}
}
%------------------------------------------------

\cventry
{Junior Web Developer} % Job title
{Viacoremedia} % Organization
{Toronto, ON} % Location
{May. 2016 - Sept. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed excellent time-management skills through deadline driven projects and tasks.}
\item {Responsible for management of web pages, email hosting, web hosting.}
\item {Responsible for creating scalable robust web pages; information gathering, planning, developing, testing, debugging code and designing interfaces.}
\item {Created multiple scalable, responsive, and robust PPC web pages with high conversion rates.}
\item {Worked with clients and project managers to determine the scope and goals of their web pages such as SEO Optimization.}
\item {Gathered and analyzed data for website optimization and presentation to the client.}
\item {Demonstrated detailed application of software knowledge through the production of a series of projects including: \\Animations (CSS3, JQuery); Scripting (PHP, Javascript, JQuery, Google Apps Scripts); CMS(Wordpress).}
\end{cvitems}
}

%------------------------------------------------
\end{cventries}